Andres Karjus &nbsp;<font size='3'> evolutionary&nbsp;linguist | cultural&nbsp;data&nbsp;analytics&nbsp;scholar | digital&nbsp;humanities&nbsp;educator </font>

### 2022-11-04 news.Rmd
news

@@

>>>>

- We received an applied research prize from the Tallinn city government for our industry collaboration project with Ekspress Group (28.09.2022) | [News piece in Estonian](https://www.tlu.ee/bfm/uudised/rakenduslike-teadustoode-konkursi-voitis-indrek-ibruse-mark-metsa-ja-andres-karjuse)

@@

- This summer I'm teaching R and data visualization workshops in 2 [summer schools](https://andreskarjus.github.io/artofthefigure/), in Latvia and Czech Republic.
